Unscrambling arrested development: temporal ordering and registration of cross-sectional imaging data

### 2014-04-09 image_analysis_paper/pnas_draft.tex
added more edits

\begin{figure}[t]
\includegraphics[width=8.4cm]{fig3}
\caption{Illustration of methodologies using one-dimensional profiles. (a) One-dimensional concentration profile on a ring (top), and the corresponding profile on a line (bottom). (b) Intensity corresponding to the profile in (a). (c) An ensemble of concentration profiles, each of the form described in (a). Each row in the array corresponds to a single image. (d) The concentration profiles in (c), now registered using angular synchronization. (e) The concentration profiles in (c), now temporally ordered using diffusion maps. (f) The concentration profiles in (c), registered and temporally ordered in a single step using vector diffusion maps.}
%\label{fig:1d_demo}
\customlabel{fig:1d_demo}{3}
\customlabel{subfig:1d_example}{\ref{fig:1d_demo}a}
\customlabel{subfig:1d_intensity}{\ref{fig:1d_demo}b}
\customlabel{subfig:1d_unaligned_unordered}{\ref{fig:1d_demo}c}
\customlabel{subfig:1d_aligned_unordered}{\ref{fig:1d_demo}d}
\customlabel{subfig:1d_aligned_ordered}{\ref{fig:1d_demo}e}
\customlabel{subfig:1d_aligned_ordered_vdm}{\ref{fig:1d_demo}f}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=8.4cm]{fig4}
\caption{(a) Set of vectors, each in a different orientation. The angles to align one vector to another are indicated. (b) The vectors from (a), each rotated so that the set is globally aligned. Note that the chosen rotation angles are consistent with the pairwise alignments in (a). (c) Data points (in black) which lie on a one-dimensional nonlinear curve in two dimensions. Each pair of data points is connected by an edge, and the edge weight is related to the Euclidean distance between the points through the diffusion kernel (see \eqref{eq:dmaps_W}), so that close data points are connected by dark (``stronger'') edges. (d) The data in (c), colored by the first (non-trivial) eigenvector from the diffusion map computational procedure, $\phi_2$. The color intensity is monotonic with the arclength, thus parameterizing the curve.  }
%\label{fig:schematics}
\customlabel{fig:schematics}{4}
\customlabel{subfig:synch1}{\ref{fig:schematics}a}
\customlabel{subfig:synch2}{\ref{fig:schematics}b}
\customlabel{subfig:dmaps_edges}{\ref{fig:schematics}c}
\customlabel{subfig:dmaps_color}{\ref{fig:schematics}d}
\end{figure}

>>>>

\begin{figure}[t]
\includegraphics[width=8.4cm]{fig3}
\caption{(a) One-dimensional concentration profile on a ring (top), and the corresponding profile on a line (bottom). (b) Intensity corresponding to the profile in (a). (c) An ensemble of concentration profiles, each of the form described in (a). Each row in the array corresponds to a single profile. (d) The profiles in (c), now registered using angular synchronization. (e) The profiles in (c), now temporally ordered using diffusion maps. (f) The profiles in (c), registered and temporally ordered in a single step using vector diffusion maps.}
%\label{fig:1d_demo}
\customlabel{fig:1d_demo}{3}
\customlabel{subfig:1d_example}{\ref{fig:1d_demo}a}
\customlabel{subfig:1d_intensity}{\ref{fig:1d_demo}b}
\customlabel{subfig:1d_unaligned_unordered}{\ref{fig:1d_demo}c}
\customlabel{subfig:1d_aligned_unordered}{\ref{fig:1d_demo}d}
\customlabel{subfig:1d_aligned_ordered}{\ref{fig:1d_demo}e}
\customlabel{subfig:1d_aligned_ordered_vdm}{\ref{fig:1d_demo}f}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=8.4cm]{fig4}
\caption{(a) Set of vectors, each in a different orientation. The pariwise alignment angles are indicated. (b) The vectors from (a), each rotated so that the set is globally aligned. Note that the chosen rotation angles are consistent with the pairwise alignments in (a). (c) Data points (in black) which lie on a one-dimensional nonlinear curve in two dimensions. Each pair of data points is connected by an edge, and the edge weight is related to the Euclidean distance between the points through the diffusion kernel (see \eqref{eq:dmaps_W}), so that close data points are connected by dark (``stronger'') edges. (d) The data in (c), colored by the first (non-trivial) eigenvector from the diffusion map computational procedure, $\phi_2$. The color intensity is monotonic with the arclength, thus parameterizing the curve.  }
%\label{fig:schematics}
\customlabel{fig:schematics}{4}
\customlabel{subfig:synch1}{\ref{fig:schematics}a}
\customlabel{subfig:synch2}{\ref{fig:schematics}b}
\customlabel{subfig:dmaps_edges}{\ref{fig:schematics}c}
\customlabel{subfig:dmaps_color}{\ref{fig:schematics}d}
\end{figure}
